\documentclass{article}
\usepackage{graphicx,amssymb,amstext,amsmath}
\begin{document}
%-----------------------------------------------------------
\title{EECS 428 Episode 4}
\author{Ian Dimayuga}
\maketitle
%-----------------------------------------------------------
\section{Exponential Flows}

\paragraph{}
Trace file analysis has yielded an average on time of $\mu = 80.2846$ seconds, and an average off time of $w = 147.7159$ seconds.
The total duration of the simulation $S = 2000$ seconds, and the number of browser flows was $n = 60$.
The total number of bytes transmitted by the exponential flows was measured to be $T = 222283500$ bytes, or approximately 212 MB.

\paragraph{}
Theoretically, the total number of bytes transmitted is given by the equation $T = \dfrac{S n \mu r}{\mu + w}$, where $r$ is the average on-time rate in bytes per second.

\paragraph{}
Solving for $r$, we get $r = 5260.53$ B/s, or about $0.04$ Mbps.

\section{Pareto Flows}
\paragraph{}
For the Pareto flows, trace file analysis yields an average on time $\mu = 0.411519$ seconds, and an average off time of $w = 24.7697$ seconds.
The total number of pareto bytes was $T = 16812900$ bytes, or approximately 16 MB.

\paragraph{}
Solving the same equation for $r$, this time we get $r = 8573.3$ B/s, or about $0.07$ Mbps.

\section{Elephant Prediction}

\paragraph{}
Given the bandwidth taken up by the Pareto and Exponential flows, the Elephants are left with $10 - r_{exp} - r_{pareto} = 9.8945$ Mbps of bandwidth through the central link.
Given that each Elephant must transmit a 400MB file, the Elephant is expected to finish at about 970s on average, given one-third of the remaining bandwidth.

\paragraph{}
The measured Elephant finish times were 704s, 885s, and 1441s. This is in keeping with the expected average finish time.

\end{document}
